\bf Service Chain Placement in SDNs \thanks{Research supported in part by Network Programming (Neptune) Consortium, Israel.}

### 2017-11-12 src/chain.tex
camera ready

The orientation phase is done as follows: let $N$ be the set of
neighborly vertices, and let $\pi:N \to \set{1,\ldots,\abs{N}}$ be a
random permutation.  We direct the edges according to $\pi$.  Observe
that each edge $e \in E$ is found on a simple path between two
neighborly nodes $v_e$ and $v'_e$, in which all internal vertices are
in $V \subseteq N$.  The edge $e$ is directed towards $v_e$, if
$\pi(v_e) > \pi(v'_e)$, and otherwise it is directed towards $v'_e$.
%
Observe that when this process terminates we get a DAG, denoted by
$G_\pi$, where there is a topological order than is consistent which
$\pi$.  Figure~\ref{fig:orientation} depicts the orientation stage.
%
A na\"ive implementation of this phase would run in $O(|V||E|)$ time.

>>>>

The orientation phase is done as follows: let $N$ be the set of
neighborly vertices, and let $\pi:N \to \set{1,\ldots,\abs{N}}$ be a
random permutation.  We direct the edges according to $\pi$.  Observe
that each edge $e \in E$ is found on a simple path between two
neighborly nodes $v_e$ and $v'_e$, in which all internal vertices are
in $V \setminus N$.  The edge $e$ is directed towards $v_e$, if
$\pi(v_e) > \pi(v'_e)$, and otherwise it is directed towards $v'_e$.
%
Observe that when this process terminates we get a DAG, denoted by
$G_\pi$, where there is a topological order than is consistent which
$\pi$.  Figure~\ref{fig:orientation} depicts the orientation stage.
%
A na\"ive implementation of this phase would run in $O(|V||E|)$ time.
